30 years of privacy research for the masses \& \newline 15 years of decentralization attempts

### 2014-03-13 paper.tex
Typo fix
Added the text about Pastry + fixed major issues
Moved the chapter about Tor vulnerabilities and attacks down, fixed
typos and removed duplicated text

			As we saw, the directory service generates overhead of the network. If we could replace this central authority, we could reduce the overhead of the network and improve the performance. This means, we would like to have Tor decentralized. Many research has been done already on the decentralization of Tor [linkjezz] but so far, no anonymous, well-performing decentralized network has come up. This is due to the fact that there are many problems decentralization brings along with.

@@

	\section{Comparison existing decentralized  networks}
		\label{sec:comparison}

		\subsection{Pastry}
			Information about Pastry.

		\subsection{Tapestry}
			Tapestry is based on the Plaxton mesh data structure [linkje naar plaxton paper], which maintains pointers to node in the network whose IDs match the elements of a tree-like structure of ID prefixes up to a digit position. A property of Tapestry is that it offers load distribution and routing locality. Tapastry is very similar to pastry [link naar pastry paper] but there are some small differences in in the handling of network locality and data replication.

@@

@@

	\section{Comparison existing decentralized networks}
		In the last section, we discussedexisting decentralized peer-to-peer networks. In this section we will make a comparison between these networks. For each network, we will explain the following features:

		\begin{itemize}
			\item{Compatibility with Tor:} If the network is compatible with Tor, the network or some features of the network could be used for the decentralization of Tor.
			\item{Public implementation:} For each network we will explain whether a public implementation is available.
			\item{Used in practice:} Is the network used in practice?
			\item{Attack resistance:} We will explain the various weaknesses and possible attacks of each network.
		\end{itemize}

>>>>

		As we saw, the directory service generates overhead on the network. If we could replace this central authority, we could reduce the overhead of the network and improve the performance. This means, we would like to have Tor decentralized. Many research has been done already on the decentralization of Tor [linkjezz] but so far, no anonymous, well-performing decentralized network has come up. This is due to the fact that there are many problems decentralization brings along with.

@@

		\subsection{Tapestry}
			Tapestry is based on the Plaxton mesh data structure [linkje naar plaxton paper], which maintains pointers to node in the network whose IDs match the elements of a tree-like structure of ID prefixes up to a digit position. A property of Tapestry is that it offers load distribution and routing locality.

@@

		\subsection{Pastry}
			Pastry is very similar to Tapestry, but there are some small differences. One of these differences is the handling of network locality and data object replication. Plastry also uses the Plaxton mesh data structure for the routing algorithm. Each peer in the network gets assigned a random 128-bit identifier that is uniform sampled from the key space. Each node can be found in about log(n) steps.

			The Pastry overlay network is used in several applications, such as Scribe, Squirrel and PAST. Scribe is an system that has been built to send multicast messages. Instead of relying on the multicast infrastructure, multicast messages are sent using only unicast services. Pastry is used to create and manage multicast groups. Scribe makes use of the organization, robustness and reliability of the Pastry network.

			Squirrel is a decentralized peer-to-peer web cache. The network uses Pastry to locate it's objects and for the routing algorithm. Squirrel allows users to share it's web cache with other users in the network, creating a large decentralized web cache. Squirrel however introduces some overhead when searching the cache. The challenge is to keep this overhead as low as possible.

			PAST is a large scale persistent peer-to-peer network that has been designed to store files. It is built upon the Pastry network and the main focus of PAST is providing performance, scalability and security.

@@

	\section{Comparison existing decentralized networks}
		In the last section, we discussed existing decentralized peer-to-peer networks. In this section we will make a comparison between these networks. For each network, we will explain the following features:

		\begin{itemize}
			\item{Compatibility with Tor:} If the network is compatible with Tor, the network or some features of the network could be used for the decentralization of Tor.
			\item{Public implementation:} For each network we will explain whether a public implementation is available.
			\item{Used in practice:} Is the network used in practice?
			\item{Attack resistance:} We will explain the various weaknesses and possible attacks of each network.
			\item{Anonimity:} Does the network hide the identities of the sender and/or receiver?
		\end{itemize}
